Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-28 src/article.tex
Add HB + CW edits to methods section

Unit tests were implemented to maintain individual elements of the source code
during development. Integration tests were written to test the Scaffolder
software interface as a whole. Unit tests were written using the Shoulda and
RSpec \cite{rspec} libraries.  Integration tests were written using the
Cucumber library \cite{rspec}. \pb

@@

The choice of nucleotide sequences comprising the scaffold is specified using
the YAML syntax \cite{yaml}. YAML is a language format using whitespace and
indentation to produce a machine readable structure. As YAML is a standardised
data format, third-party developers have the option to generate a genome
scaffold using any programming language for which a YAML library exists. The
YAML website lists current parsers for languages including C/C++, Ruby, Python,
Java, Perl, C\#/.NET, PHP, and JavaScript. In addition to being widely
supported YAML formatted scaffold files can be validated for correct syntax
using third party tools such as Kwalify \cite{kwalify}. \pb

As described in the Background section, the initial sequencing data assembly
may result in an incomplete genome build. The use of computational software and
generation of additional sequence using PCR means genome scaffolding may be an
on-going process. Therefore the scaffold file should be simple to update
manually in addition to being computationally tractable. This requirement was
therefore the second reason YAML was selected, where YAML is human-readable and
simple to edit in a standard text editor. \pb

The scaffold file takes the form of a list of entries. Each entry corresponds
to a region of sequence, most likely a contig or previously scaffolded set of
contigs. The Scaffolder software processes this list in order, converting each
to the corresponding nucleotide sequence. These nucleotide sequences are then
concatenated to produce a draft super sequence. Each entry in the scaffold file
may have attributes that define whether a sub-sequence or the reverse
complement of the sequence should be used. The types of attributes available,
and an example scaffold file are outlined in the Results and Discussion section
below.  \pb

>>>>

Unit tests were implemented to maintain individual elements of the source code
during development and were written using the Shoulda and RSpec \cite{rspec}
libraries. Integration tests were written to test the Scaffolder software
interface as a whole and were written using the Cucumber library \cite{rspec}.
\pb

@@

The choice of nucleotide sequences comprising the scaffold is specified using
the YAML syntax \cite{yaml}. YAML is a language format using whitespace and
indentation to produce a machine readable structure. As YAML is a standardised
data format, third-party developers have the option to generate a genome
scaffold using any programming language for which a YAML library exists. The
YAML website lists current parsers for languages including C/C++, Ruby, Python,
Java, Perl, C\#/.NET, PHP, and JavaScript. In addition to being widely
supported, YAML-formatted scaffold files can be validated for correct syntax
using third-party tools such as Kwalify \cite{kwalify}. \pb

Initial sequencing data assembly may result in an incomplete genome build.
Generation of additional sequences either through PCR or computational methods
means that genome scaffolding may be an on-going process. The scaffold file
should therefore be simple to update manually in addition to being
computationally tractable. This requirement was also best suited to YAML which
is human-readable and simple to edit in a standard text editor. \pb

The scaffold file takes the form of a list of entries. Each entry corresponds
to a region of sequence inserted from the corresponding fasta file. The
Scaffolder software processes this list in order, converting each to the
corresponding nucleotide sequences, which are then concatenated to produce
a draft super sequence. Each entry in the scaffold file may have attributes
that define whether a sub-sequence or the reverse complement of the sequence
should be used. The types of attributes available, and an example scaffold file
are outlined below. \pb
